%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\setlength{\footskip}{4.35004pt}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Multi Columns
\usepackage{multicol}
\setlength{\columnsep}{1cm}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\normalsize{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%------------RESUME STARTS HERE-------------

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}c r}
  \textbf{\href{https://github.com/ericvtheg/}{\Large Eric Ventor}} & (818) 398-4136 & \href{https://github.com/ericvtheg}{GitHub.com/ericvtheg}  \\
  {Los Angeles, California} & \href{mailto:ericventor97@gmail.com}{ericventor97@gmail.com} & \href{https://www.linkedin.com/in/ericventor}{LinkedIn.com/in/ericventor} \\
\end{tabular*}

%-----------OBJECTIVE-----------------
\section{Professional Summary}
{A results-driven \textbf{Fullstack Software Engineer} with 6 years of proven excellence in delivering high-impact solutions. Recognized as a top performer who consistently translates complex technical challenges into measurable business outcomes. Known for fostering collaborative environments and committed to pushing boundaries.} 
% 

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Software Engineer IV}{Apr. 2021 - Present}
{iFIT - Interactive at Home Fitness}{Remote}
\resumeItemListStart
\resumeItem{Project Leadership}
{Led and implemented a goals service supporting 100,000+ concurrent users, resulting in a 25\% reduction in user churn rate. Youngest employee to lead a major project from inception to completion.}
\resumeItem{Distributed Systems}
{Architected and developed an event-driven microservice architecture using NestJS, AWS Kinesis, containers, and MongoDB, supporting 1 million monthly active users.}
\resumeItem{Business Impact Focus}
{Championed a shift from feature-quantity focus to measurable user and business impact across the organization, leveraging data analytics to drive product decisions.}
\resumeItem{Mentorship and Leadership}
{Provided guidance to junior employees on architectural and development decisions, promoting a balance of pragmatism and extendability.}
\resumeItem{Incident Management}
{Coordinated team responses to system outages, resulting in timely resolutions and minimal user impact. Presented blameless postmortems and improved service observability to accelerate incident response times.}
\resumeItemListEnd

\resumeSubheading
{Media Software Engineer} {Jul. 2020 - Apr. 2021}
{Disney - Media \& Entertainment Distribution}{Remote}
\resumeItemListStart
\resumeItem{Media Hub}
{Maintained and contributed to an Emmy award winning web app used daily by over a 1,000 Disney employees. The app provides an e2e solution for managing media assets.}
\resumeItem{Service Deprecation}
{Saved \$120,000+ annually by leading the replacement of a monolithic service to a serverless event driven architecture.}
\resumeItemListEnd

\resumeSubheading
{Co-founder \& CTO} {Feb. 2019 - Jul. 2020}
{Sphere Influencer - Social Media Marketing}{Los Angeles, CA}
\resumeItemListStart
\resumeItem{Mona SaaS}
{Generated +\$1,500 in MRR by developing a full-stack web app for influencer marketing campaigns. Utilized React, AWS serverless technologies, and Elasticsearch.}
\resumeItemListEnd

\resumeSubHeadingListEnd

% -----------PROJECTS-----------------
\section{Personal Projects}
\resumeSubHeadingListStart
\resumeSubItem{MAKID}
{Develop and maintain a desktop music management application using Electron.js, having grown it from zero to 1,000+ Monthly Active Users. Leverage Mixpanel analytics to drive data-informed business decisions and guide feature development.}

\resumeSubItem{Technical Blog}
{Contribute to my blog, \href{EricVentor.com}{EricVentor.com}, where I write about personal projects, learnings, and general tech.}
%\resumeSubItem{\href{BetaTestSongs.com}{BetaTestSongs.com}}
%{Created a fullstack web app using React, NestJS, and PostgreSQL, where music producers can upload their songs to be critiqued.}
\resumeSubHeadingListEnd

%--------ADDITIONAL SKILLS------------
\section{Technical Expertise}
\vspace{-15pt}
\resumeSubHeadingListStart
\begin{multicols}{2}
  \item{
              \textbf{Languages}{: Typescript, Python, SQL}}
  \vspace{-5pt}
  \item{
              \textbf{Backend}{: Node.js, NestJS, REST, GraphQL, Containers, Serverless }}
  \vspace{-5pt}
  \item{
              \textbf{Frontend}{: React, Next.js, Electron, Vite, Tailwind CSS}}
  \vspace{15pt}
  \item{
              \textbf{Databases}{: PostgreSQL, MongoDB, Snowflake, Vector Stores, DynamoDB, Elasticsearch}}
  \vspace{-5pt}
  \item{
      \textbf{Tools}{: LLMs (ChatGPT \& Claude), Mixpanel, LangChain, Docker, Datadog, Git, Jest, Terraform, }}
  \vspace{-5pt}
  \item{
              \textbf{AWS Services}{: RDS, S3, IAM, ECS, EC2, Fargate, Lambda, Kinesis, CloudFront, SNS, SQS, API Gateway }}

\end{multicols}
\vspace{-30pt}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of California, Santa Cruz}{Santa Cruz, CA}
{Bachelors of Science in Computer Science}{Sept. 2015 - Jun. 2019}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
